Is statistical significance a thing?

### 2018-04-05 doc.tex
a few tweaks

\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) has resulted in
calls to abandon its use. Alternatively, we argue that statistical hypothesis tests are useful, but are not, and should not
be referred to, as tests of significance. We propose that a sensible method to reduce misconceptions about NHST and p~values 
is to refer to the results of NHST (i.e. $p < or > 0.05$) using ``statistical clarity''. A test of the null hypothesis tells 
us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
negative, or if a response in the treatment group is greater than the response in the control group). Specifically, we argue 
that the use of ``statistical clarity'' will help researchers avoid accepting the null hypothesis and reclaim the English 
definition for ``significance'', allowing for a shift in focus to substantive significance.

@@

Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016},
we conclude with a plea for an increased emphasis on effect sizes and confidence intervals. However, we suggest that the
use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing all ambiguity
from statements associated with $p < 0.05$. The statement ``The difference between our control and treatment groups were
statistically clear ($p = 0.007$)'' in unambiguously incomplete and uncompelling; an effect size and confidence interval 
is required to complete the story.

>>>>

\textbf{Abstract}: Decades of misuse and misinterpretation of Null Hypothesis Significance Testing (NHST) have resulted in
calls to abandon its use. Alternatively, we argue that statistical hypothesis tests are useful, but are not, and should not
be referred to, as tests of significance. We propose a simple method to reduce misconceptions about NHST and p~values: 
refer to the results of NHST (i.e. $p <$ or $> 0.05$) using ``statistical clarity'' rather than ``statistical significance''. A test of the null hypothesis tells 
us whether or not we can \emph{clearly} see our effect (e.g. whether we can clearly see that a correlation is positive or 
negative, or if a response in the treatment group is greater than the response in the control group). Specifically, we argue 
that the use of ``statistical clarity'' will help researchers avoid accepting the null hypothesis and reclaim the English 
definition for ``significance'', allowing for a shift in focus to substantive significance.

@@

Following the lead of \citet{Cohen1994} and others \citep{Goodman1999, ZiliakandMcCloskey2008, WassersteinandLazar2016},
we conclude with a plea for an increased emphasis on effect sizes and confidence intervals. However, we suggest that the
use of ``statistical clarity'' forces the \emph{need} for confidence intervals and effect sizes by removing ambiguity
from statements associated with $p < 0.05$. The statement ``The difference between our control and treatment groups was
statistically clear ($p = 0.007$)'' is unambiguously incomplete; an effect size and confidence interval 
is required to complete the story.
